The globular cluster system of the Auriga simulations

### 2019-08-20 AurigaGCS_20190820.tex
Updated version

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy and star formation model used for the Auriga simulations
can produce a realistic globular cluster (GC) population. We compare statistics 
of GC candidate star particles in the Auriga haloes with catalogues of the Milky 
Way (MW) and Andromeda (M31) globular cluster populations. We find that the Auriga 
simulations do produce sufficient stellar mass for GC candidates at radii and 
metallicities that are typical for the MW GC system (GCS), although we observe a 
varying mass-ratio for different galactocentric radius-metallicity 
($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates relative to the 
observed mass in the MW and M31 GC systems.
This implies different values for the combined product of the bound cluster 
formation efficiency and the GC disruption rate. Furthermore we test whether any of the 
Auriga galaxies has a metallicity and radial distribution that is consistent with 
the MW or M31 GCS. For any one of the Auriga haloes we reject the null hypothesis
that the observed and simulated metallicities of GCs (GC candidates) are drawn
from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
the MW and M31. The same holds true for the distribution of $R_{\text{gal}}$.
Overall, the Auriga simulations produce GC candidates with higher metallicities 
than the MW and M31 GCS and at larger radii. This implies that the bound cluster
formation efficiency would have to decrease with increasing metallicity for the 
Auriga GC candidates to be consistent with the MW GCS, if GC disruption is equally 
efficient regardless of metallicity. In addition, the number of GCs relative to
field stars would have to be smaller for higher metallicity star particles at
large radii than for those with lower metallicity at smaller radii, assuming GC 
disruption is more efficient in the inner regions of the Galaxy.
\end{abstract}

@@

Yet another hypothesis is that star cluster formation is triggered by major 
gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and are found to show 
remarkable similarities with GCs in the MW \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
produces star clusters that could be globular progenitors \citep{
2019arXiv190509840L}.

@@

The Auriga suite has a fiducial baryonic mass resolution $m_b$~=~$5 \times 10^4$~M\Sun,
with gravitational softening of collissionless particles $\epsilon$~=~369~pc.
Simulations at this resolution are referred to as level 4 (L4). Selected
initial condition runs are acompanied by the lower (higher) resolution level L5 (L3).
The resolution for these levels is $m_b$~=~$4 \times 10^5$~M\Sun \, with 
$\epsilon$~=~738~pc, and $m_b$~=~$6 \times 10^3$~M\Sun \, with $\epsilon$~=~184~pc,
respectively. The mass resolution of the Auriga simulations is thus close to the 
characteristic peak mass of the lognormal GC mass distribution of $10^{5}$~M\Sun 
\citep{1991ARA&A..29..543H}, although the gravitational softening is two orders 
of magnitudes larger than typical GC radii of several parsec. High-density gaseous 
regions are thus not expected to produce surviving stellar clumps with masses and 
radii consistent with GCs because such objects would numerically disperse, even 
in the highest-resolution runs. On the other hand, we can investigate (statistical) 
properties of age-selected GC candidates because each star particle represents a
single stellar population with a total mass that could be consistent with one 
globular cluster. This means that their formation sites and that of a real-world 
GC may be consistent.

@@

We find that the age cut, on average, lowers the mean metallicity [Fe/H] from 
$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
metallicities than the {\it in~situ} subset with differences of roughly
${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
for which the {\it in~situ} subset has a lower mean metallicity instead. 
\mbox{Au4-1} is undergoing a major merger at redshift zero and we find 
$\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} (accreted) GC candidates, 
although the former consists of only $1019$ particles ($1.3$\% of all GC 
candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
has undergone a major merger around 2~Gyr lookback time, which is probably why
the accreted population is more metal rich. After inspection of the same figure 
for every one of the thirty Auriga L4 haloes we find that the simulations produce
(sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
Moreover, none of the simulations has a (total) population of GC 
candidates with a bimodal metallicity distribution.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median for all thirty Auriga L4 haloes with the $1\sigma$ interval around it 
(shaded regions, which shows the scatter between runs that have different initial 
conditions, thus, have unique merger histories). We chose to aggregate the data 
to indicate general trends that we find when the GC candidates are split up into
the accreted and {\it in situ} subsets, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
and we find that the mass at the peak lowers by roughly one dex. The mass budget 
of the GC candidates is dominated by the {\it in~situ} subpopulation above
[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW (M31) 
GCS in purple (magenta) and notice that the difference between the MW and M31 
distributions is substantially larger than the scatter between different Auriga 
galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
the MW does not.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (blue solid), and those that 
        were accreted (red solid). Shaded regions indicate the $1\sigma$ 
        interval. The MW (M31) GCS is shown in purple (magenta). The middle 
        (bottom) panel shows the ratio of the simulated mass to the mass in the 
        MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed {\it in~situ} to the accreted population around
$10$~kpc. Again we show the mass ratio of the simulations compared to the MW 
and M31 GCS. We find a decreasing mass ratio with increasing radius
in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
to the accreted subpopulation. For the MW we notice that significantly
fewer GCs are found beyond $40$~kpc than for M31, and that accreted GC candidates
contribute mostly to the Auriga GCS at these radii. We further investigate a 
breakdown of the total mass in Auriga GC candidates into bins of both metallicity 
and radius in the following section.

@@

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
we sum the total mass of GC candidates in each bin (for an individual Auriga 
simulation), then we calculate the median total mass in each bin over all 
thirty Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc} (which 
can be compared to the observed total GC mass shown in 
Figure~\ref{fig:observations_FeHRgc}). We notice that the Auriga simulations, 
on average, produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) 
than at higher metallicities in the three innermost radial bins. In addition, 
Auriga produces fewer high-metallicity GCs at large radii, similar to the MW 
and M31 GCSs.

To ease the comparison between the simulations and observations we take the ratio
of the total mass of GC candidates in Auriga to the total GC mass in the MW 
(and M31). We use a diverging colour map centered around the overall median of the 
mass ratio (i.e. we subtract the median of these twenty-five bins from the value 
in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
Note that the data in three top right bins is masked because the mass ratio cannot 
be calculated due to zero mass in the observations (therefore the bins are white).
If the product of the bound cluster formation efficiency and consecutive GC 
disruption over a Hubble time would be constant, then the value in each bin would
have been zero. The red and blue bins indicate deviations from such as scenario and
indicate a higher and lower than average mass excess. In particular, the median 
value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
respectively. This means that the overall `mass budget' that the simulations `can 
afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
The lowest mass surplus for both galaxies is the the bin where $-2.5 <$ [Fe/H] 
$< -1.5$ and $3 < R_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
more mass in GC candidates than what is observed in the MW and M31 respectively.
The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
for M31.

The top panel of Figure~\ref{fig:Au-FeHRgc-ratio} shows that mass excess for
Auriga GCs within the Solar radius decreases with decreasing metallicity. This
means that either the formation efficiency should increase with decreasing metallicity,
or that the lowest-metallicity GCs in the Auriga simulations are less strongly affected
by disruptive processes, if the star formation histories in the Auriga simulations
are to give rise to a GCS that can be similar to the GCS that is observed
in the MW. Moreover, either a lower formation efficiency is required at
large radii, or stronger disruption. Disruption of star clusters is expected to
be more efficient at smaller radii due to higher tidal forces in the innermost
region for GCs on orbits that pass through the disk, or with pericenters close 
to the bar or bulge. Compared to M31, the mass ratio (bottom panel of 
Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trend than for the MW,
which suggests that both galaxies have diverse GC formation histories.
Most bins show mass surplus factors of few tens, meaning that high formation 
efficiencies would be required in addition to little disruption for the Auriga 
simulations to yield a GCS consistent with that of M31.

@@

\section{Discussion}
\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
Globular clusters are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
selection function (age cut) does lower the mean metallicity of GC candidates by 
$0.5$ dex with respect to all star particles, but we still find that the GC 
candidates in the Auriga simulations are more metal-rich than the MW and M31 GCSs. 
Although the (old) star particles represent single stellar populations with a mass 
consistent with that of GCs, they are in fact statistical tracers 
of the stellar population of the galaxy as a whole. Therefore only a (small) 
fraction of the star particles may represent plausible formation sites of GCs, 
whereas the majority represents (halo) field stars - the disk component effectively 
falls outside our selection of star particles due to the age cut. It is implausible 
that all halo stars come from disrupted GCs because the total mass in GCSs 
at redshift zero is generally a few orders of magnitude lower than the total 
mass of stellar haloes of galaxies. If stellar haloes solely consist of disrupted
GCs, then the GC disruption rate would have to be considerably higher than expected
from theoretical models. Overall, our set of GC candidates most likely contains
an overabundance of regular stars. It could be that the resulting metallicity
distribution is then biased towards higher values than what is observed for real 
GCs. An alternative explanation could overmixing of metals at early times.

@@

We find that none of the Auriga simulations produces a bimodal 
metallicity distribution for age-selected GC candidates. Interestingly, the 
cross-over point above (below) which the mass-weighted metallicity distribution
of GC candidates is dominated by those that have formed {\it in~situ} (were
accreted) does coincide with the separation between the metal-rich and metal-poor
populations of GCSs at [Fe/H]~=~$-1$, as for the MW. Moreover, we do find 
that the mean metallicity shifts when we split the GC candidates up according 
to birth location (accreted or {\it in~situ}). In particular, the mean values of 
the {\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
However, we also notice that a substantial number of simulations has similar 
mean values for all GC candidates, and the simulated {\it in~situ} GC candidates 
have larger dispersions than the metal-rich GCs. Moreover, the offset between 
the mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a
factor $2-3$ larger than the offset that we find between the {\it in~situ} and 
accreted populations. The Auriga simulations therefore do not support the view 
that the metal-poor GCs could have only formed in satellites that have later been 
accreted whereas the metal-rich GC subpopulation has only formed {\it in~situ}. 
With this statement, however, we do caution that \citet{2019MNRAS.486.3134K} suggests 
to reserve the `{\it ex~situ}' classification for accretion after $z=2$, when
the central galaxy has formed and accretion unambigously contributes to the
radially extended halo GC population. In fact, our classification might not hold
for Au4-1.

Finally, we note that \citet{2006ARA&A..44..193B} compares the number of metal-poor 
GCs to the stellar halo mass and find\footnote{The quantity $T$ is the number of 
GCs per $10^9$ M\Sun \, of galaxy stellar mass.} $T^n_{\text{blue}} \sim 100$, 
while the number of metal-rich GCs compared to the bulge mass yields 
$T^n_{\text{red}} \sim 5$, and therefore conclude that the formation efficiency
of metal-poor GCs is twenty times higher than the metal-rich GCs with respect to 
field stars. We find that a gradual increase in formation efficiency of GCs
with respect to field stars would be required with decreasing metallicity for
the GC candidates in the Auriga simulations to yield sufficient total mass to
be consistent with the MW or M31 GCS.

\subsection{Radial distribution}
\label{sec:discussion_Rgc}
The M31 GCS has a factor 2-3 more GCs at large radii compared to the MW GCS,
which may indicate that M31 has a richer merger history than the MW 
\citep{2016ApJ...824...42C}. In the Auriga simulations we find that the GC 
candidates at radii larger than ${\sim}20$~kpc are indeed dominated by accreted
star particles. However, we select star particles that are bound to the main 
halo and main subhalo, which means that we include particles up to the virial 
radius $R_{200}$. The Auriga simulations have no problem populating the stellar 
halo up to the virial radius, even with our additional age cut. On the other hand, 
the MW and M31 have fewer GCs at large radii. We expect tidal disruption to be
less efficient at larger radii, thus, the formation efficiencies of the accreted 
GC candidates would have to be lower. Our classification as GC candidates could, 
for example, be improved by selecting a number of globular clusters based on the 
$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}, and 
taking a virial mass below which none of the star particles is treated as GC candidate.

@@

We investigate GC candidates in the Auriga simulations and draw the following
conclusions.

\begin{itemize}
    \item The star formation model implemented in the Auriga simulations produces
    metallicity distributions that are more metal-rich than the MW and M31
    GCSs.

    \item We reject the null hypothesis $H_0$ for any one of the Auriga simulations 
    that the GC candidates and the MW GCs are drawn from the same underlying 
    distribution. This statement holds true when we select all old star particles 
    (GC candidates), but also when we select the old accreted or the old {\it in~situ} 
    star particles. In addition, this is also the case when we test against the 
    M31 GCS instead of the MW GCS. Moreover, the difference between the MW and
    M31 is big compared to the scatter in GC candidate properties in the Auriga
    simulations.

>>>>

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy and star formation model used for the Auriga
simulations can produce a realistic GC population. We compare statistics of GC 
candidate star particles in the Auriga haloes with catalogues of the Milky Way 
(MW) and Andromeda (M31) GC populations. We find that the Auriga simulations do 
produce sufficient stellar mass for GC candidates at radii and metallicities that 
are typical for the MW GC system (GCS). We do observe varying mass-ratios of the
simulated GC candidates relative to the observed mass in the MW and M31 GC systems
for different bins of galactocentric radius-metallicity ($R_{\text{gal}}$-[Fe/H]).
This implies that different values for the combined product of the bound cluster 
formation efficiency and the GC disruption rate are needed. Overall, the Auriga 
simulations produce GC candidates with higher metallicities than the MW and M31 
GCS and they are found at larger radii than observed. Bound cluster formation
efficiencies higher than ten percent are needed for the metal-poor GC candidates,
and those within the Solar radius should experience negligible destruction rates.
GC candidates in the outer halo, on the other hand, should either have low formation
efficiencies, or experience high mass loss for the Auriga simulations to produce a
GCS that is consistent with that of the MW or M31. Finally, the scatter in the 
metallicity as well as in the radial distribution between different Auriga runs 
is considerably smaller than the differences between that of the MW and M31 GCSs. 
The Auriga model is unlikely to give rise to a GCS that can be consistent with
both galaxies.
\end{abstract}

@@

Yet another hypothesis is that star cluster formation is triggered by major 
gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and are found to show 
remarkable similarities with GCs in the MW \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
produces star clusters that could be GC progenitors \citep{
2019arXiv190509840L}.

@@

The Auriga suite has a fiducial baryonic mass resolution $m_b$~=~$5 \times 10^4$~M\Sun,
with gravitational softening of collissionless particles $\epsilon$~=~369~pc.
Simulations at this resolution are referred to as level 4 (L4). Selected
initial condition runs are acompanied by the lower (higher) resolution level L5 (L3).
The resolution for these levels is $m_b$~=~$4 \times 10^5$~M\Sun \, with 
$\epsilon$~=~738~pc, and $m_b$~=~$6 \times 10^3$~M\Sun \, with $\epsilon$~=~184~pc,
respectively. The mass resolution of the Auriga simulations is thus close to the 
characteristic peak mass of the lognormal GC mass distribution of $10^{5}$~M\Sun 
\citep{1991ARA&A..29..543H}, although the gravitational softening is two orders 
of magnitudes larger than typical GC radii of several parsec. High-density gaseous 
regions are thus not expected to produce surviving stellar clumps with masses and 
radii consistent with GCs because such objects would numerically disperse, even 
in the highest-resolution runs. On the other hand, we can investigate (statistical) 
properties of age-selected GC candidates because each star particle represents a
single stellar population with a total mass that could be consistent with one GC. 
This means that their formation sites and that of a real-world GC may be consistent.

@@

We find that the age cut, on average, lowers the mean metallicity $<$[Fe/H]$>$ from 
$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
metallicities than the {\it in~situ} subset with differences of roughly
${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
for which the {\it in~situ} subset has a lower mean metallicity instead. 
\mbox{Au4-1} is undergoing a major merger at redshift zero and we find 
$\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} (accreted) GC candidates, 
although the former consists of only $1019$ particles ($1.3$\% of all GC 
candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
has undergone a major merger around 2~Gyr lookback time, which is probably why
the accreted population is more metal rich. After inspection of the same figure 
for every one of the thirty Auriga L4 haloes we find that the simulations produce
(sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
Moreover, none of the simulations produces GC candidates with a bimodal metallicity 
distribution.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median for all thirty Auriga L4 haloes with the $1\sigma$ interval around it 
(shaded regions, which shows the scatter between runs that have different initial 
conditions, thus, have unique merger histories). We chose to aggregate the data 
to indicate general trends that we find when the GC candidates are split up into
the accreted and {\it in situ} subsets, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
and we find that the mass at the peak lowers by roughly one dex. The mass budget 
of the GC candidates is dominated by the {\it in~situ} subpopulation above
[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW (M31) 
GCS in purple (magenta) and notice that the difference between the MW and M31 
distributions is substantially larger than the scatter between different Auriga 
galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
the MW does not.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (blue solid), and those that 
        were accreted (red solid). Shaded regions indicate the $1\sigma$ 
        interval. The MW (M31) GCS is shown in purple (magenta). The middle 
        (bottom) panel shows the ratio of the simulated mass to the mass in the 
        MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed {\it in~situ} to the accreted population around
$10$~kpc. Again we show the mass ratio of the simulations compared to the MW 
and M31 GCS. We find a decreasing mass ratio with increasing radius
in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
to the accreted subpopulation. For the MW we notice that significantly
fewer GCs are found beyond $40$~kpc than for M31, and that accreted GC candidates
contribute mostly to the Auriga GCS at these radii. We further investigate a 
breakdown of the total mass in Auriga GC candidates into bins of both metallicity 
and radius in the following section.

@@

We investigate whether the Auriga simulations still produce sufficient mass when
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{gal}$. First
we sum the total mass of GC candidates in each bin (for an individual Auriga 
simulation), then we calculate the median total mass in each bin over all 
thirty Auriga L4 haloes. The result is shown in Figure~\ref{fig:Au-FeHRgc}, which 
can be compared to the observed total GC mass shown in 
Figure~\ref{fig:observations_FeHRgc}.

To ease this comparison between the simulations and observations we take the ratio
of the total mass of GC candidates in Auriga to the total GC mass in the MW 
(and M31). We use a diverging colour map centered around the overall median of the 
mass ratio (i.e. we subtract the median of these twenty-five bins from the value 
in each bin). We show this in the top (bottom) panel of Figure~\ref{fig:Au-FeHRgc-ratio}.
Note that the data in the three top right bins is masked because the mass ratio cannot 
be calculated due to zero mass in the observations (therefore the bins are white).
If the product of the bound cluster formation efficiency and consecutive GC 
disruption over a Hubble time would be constant, then the value in each bin would
have been zero. The red and blue bins indicate deviations from such as scenario and
indicate a higher and lower than average mass excess in the simulations. The median 
value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
respectively. This means that the median `mass budget' that the simulations `can 
afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
The lowest mass surplus for both galaxies is the the bin where $-2.5 <$ [Fe/H] 
$< -1.5$ and $3 < R_{\text{gal}}/\text{kpc} < 8$, for which the simulations produce 
a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
more mass in GC candidates than what is observed in the MW and M31 respectively.
The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
for M31.

We now focus on four quadrants of this diagram, split at [Fe/H]~=~-1 (metal-poor 
or metal-rich) and $R_\text{gal}$~=~8~kpc (inside or outside the Solar radius).
The majority of the mass in Auriga GC candidates is produced in metal-rich star
particles inside the Solar radius. The total mass is dominated by the {\it in situ} 
component, for [Fe/H] as well as for $R_\text{gal}$. The total mass excess in 
this region increases with decreasing metallicity for the MW and M31, and there
is a weak trend of decreasing over-production with increasing radius for the
{\it in situ} subsets but no trend with radius for the accreted GC candidates.
As for the metal-rich GC candidates outside the Solar radius, we find that the
mass excess with respect to the median is largest in this corner for the MW and
M31. The main reason for this trend are the lower GC counts in the observations,
whereas the Auriga simulations efficiently form metal-rich GC candidates and
have no problem to produce them at large radii. The opposite is true for the
metal-poor GC candidates inside the Solar radius, where the mass surplus with
respect to the median is smallest for both galaxies. However, the disruption rates
are expected to be particularly high for GCs in the inner regions of galaxies
that are on orbits with pericentres close to the galactic bulge or bar. In addition, 
disk crossings in this region will cause spikes in the tidal tensor due to steep
density gradients that could be highly disruptive to the GCs. The bins with the 
lowest `mass budget' are in this region (a factor 9 for the MW and 22 for M31).
The bound cluster formation efficiency has to exceed 10\%, and none of the GC 
candidates in this region can experience significant mass loss in order for Auriga
to produce sufficient mass in this quadrant. Finally, the metal-poor GC candidates
outside the Solar radius have lower than average mass ratios, which is not 
surprising given that the Auriga simulations overall underproduce low-metallicity
stars particles.

@@

\section{Discussion}
\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
GCs are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
selection function (age cut) does lower the mean metallicity of GC candidates by 
$0.5$ dex with respect to all star particles, but we still find that the GC 
candidates in the Auriga simulations are more metal-rich than the MW and M31 GCSs. 
Although the (old) star particles represent single stellar populations with a mass 
consistent with that of GCs, they are in fact statistical tracers 
of the stellar population of the galaxy as a whole. Therefore only a (small) 
fraction of the star particles may represent plausible formation sites of GCs, 
whereas the majority represents (halo) field stars - the disk component effectively 
falls outside our selection of star particles due to the age cut. It is implausible 
that all halo stars come from disrupted GCs because the total mass in GCSs 
at redshift zero is generally a few orders of magnitude lower than the total 
mass of stellar haloes of galaxies. If stellar haloes solely consist of disrupted
GCs, then the GC disruption rate would have to be considerably higher than expected
from theoretical models. Overall, our set of GC candidates most likely contains
an overabundance of regular stars. It could be that the resulting metallicity
distribution is then biased towards higher values than what is observed for real 
GCs. An alternative explanation could overmixing of metals at early times.

@@

However, we find that none of the Auriga simulations produces a bimodal 
metallicity distribution for age-selected GC candidates. Interestingly, the 
cross-over point above (below) which the mass-weighted metallicity distribution
of GC candidates is dominated by those that have formed {\it in~situ} (were
accreted) does coincide with the separation between the metal-rich and metal-poor
populations of GCSs at [Fe/H]~=~$-1$, as for the MW. Moreover, we do find 
that the mean metallicity shifts when we split the GC candidates up according 
to birth location (accreted or {\it in~situ}). In particular, the mean values of 
the {\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
On the other hand, we also notice that a substantial number of simulations has similar 
mean values for all GC candidates, and the simulated {\it in~situ} GC candidates 
have larger dispersions than the metal-rich GCs. Moreover, the offset between 
the mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a
factor $2-3$ larger than the offset that we find between the {\it in~situ} and 
accreted populations. The Auriga simulations therefore do not support the view 
that the metal-poor GCs could have only formed in satellites that have later been 
accreted whereas the metal-rich GC subpopulation has only formed {\it in~situ}. 
With this statement, however, we do caution that \citet{2019MNRAS.486.3134K} suggests 
to reserve the `{\it ex~situ}' classification for accretion after $z=2$, when
the central galaxy has formed and accretion unambigously contributes to the
radially extended halo GC population. In fact, our classification might not hold
for Au4-1.

Finally, we note that \citet{2006ARA&A..44..193B} compares the number of metal-poor 
GCs to the stellar halo mass and find\footnote{The quantity $T$ is the number of 
GCs per $10^9$ M\Sun \, of galaxy stellar mass.} $T^n_{\text{blue}} \sim 100$, 
while the number of metal-rich GCs compared to the bulge mass yields 
$T^n_{\text{red}} \sim 5$, and therefore conclude that the formation efficiency
of metal-poor GCs is twenty times higher than the metal-rich GCs with respect to 
field stars. We find that a gradual increase in formation efficiency of GCs
with respect to field stars would be required with decreasing metallicity for
the GC candidates in the Auriga simulations to yield sufficient total mass to
be consistent with the MW or M31 GCS. In addition, the metal-poor GC candidates
would have to experience low mass los rates, especially those within the Solar
radius.

\subsection{Radial distribution}
\label{sec:discussion_Rgc}
The M31 GCS has a factor 2-3 more GCs at large radii compared to the MW GCS,
which may indicate that M31 has a richer merger history than the MW 
\citep{2016ApJ...824...42C}. In the Auriga simulations we find that the GC 
candidates at radii larger than ${\sim}20$~kpc are indeed dominated by accreted
star particles. However, we select star particles that are bound to the main 
halo and main subhalo, which means that we include particles up to the virial 
radius $R_{200}$. The Auriga simulations have no problem populating the stellar 
halo up to the virial radius, even with our additional age cut. On the other hand, 
the MW and M31 have fewer GCs at large radii. We expect tidal disruption to be
less efficient at larger radii, thus, the formation efficiencies of the accreted 
GC candidates would have to be lower. Our classification as GC candidates could
especially be improved for the accreted subset. For example, we could tag only a
subset of the accreted star particles as GC candidates, where the number
number of GCs is determined by the satellite halo mass, given the 
$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}.

@@

We investigate statistics of age-selected ($>$~10~Gyr) GC candidates in the 
Auriga simulations and compare the simulations to the MW and M31 GCSs. Based on
our analysis we draw the following conclusions.

\begin{itemize}
    \item The star formation model implemented in the Auriga simulations produces
    metallicity distributions that are more metal-rich than the MW and M31
    GCSs. For most of the Auriga simulations we find that the subset of accreted 
    GC candidates has a lower mean metallicity than the {\it in situ} subpopulation.
    However, the accreted subsets are still more metal-rich than the MW and M31 GCSs.
    Moreover, none of the simulated subsets has a mean metallicity as low as the mean
    of the `blue' metal-poor component of the MW GCS.

    \item We find that the difference between the metallicity distributions of 
    the MW and M31 GCSs is big compared to the scatter in the Auriga GC candidates 
    of different Auriga runs. The radial distributions of the MW and M31 GCSs are
    somewhat more similar, but they are not consistent with being drawn from the
    same distribution. The scatter between the radial distributions of different
    Auriga simulations is smaller than the difference between the MW and M31 GCSs.
